### 2020-01-02 frontmatter.tex
dipolar and soap figs

%-------------------------------------------------------------------------------
% Preface page
%-------------------------------------------------------------------------------
%
\begin{preface}
	This thesis summarizes a selection of studies on droplet interactions and suspension flows
        that may find applications in microfluidics, rheology, and soft matter physics.
        A brief introduction of some basic physical concepts and numerical methods is presented in Part I,
        followed by eight journal articles or preprints in Part II, see below.
        For consistency, all papers are formatted in the \texttt{jfm} style as the rest of the thesis.
        Their contents remain faithful to the original publications.
\end{preface}

>>>>

%-------------------------------------------------------------------------------
% Preface page
%-------------------------------------------------------------------------------
%
\begin{preface}
	This thesis summarizes a selection of studies on droplet interactions and suspension flows
        that may find applications in microfluidics, rheology, and soft matter.
        A brief introduction of basic physical concepts and numerical methods is presented in Part I,
        followed by eight journal articles or preprints in Part II, see below.
        For consistency, all papers are formatted in the \texttt{jfm} style as the rest of the thesis.
        Their contents remain faithful to the original publications.
\end{preface}

### 2020-01-02 overview.tex
dipolar and soap figs

The preceding section presents the most basic solutions of the Stokes equation in the presence of only one particle.
In practice, however, it is rarely the case particles or droplets exist in isolation.
Particles tend to abound; and they often interact with each other through various types of hydrodynamic or non-hydrodynamic mechanisms, giving rise to a multitude of phenomena in natural or artificial conditions.
For example, soap bubbles are always in a cluster due to the interfacial capillary attraction, while the same underlying principle can be applied to manipulate droplet motions on a surface to aid liquid handling \citep{vapour-sensing}.
To offer at least some partial insights on the hydrodynamics, we highlight recent theoretical developments of droplet interactions in bulk microflows, starting from the simplest case of two particles immersed in unbounded simple shear flows.

@@

\begin{figure}%[t]
  \centering
  \includegraphics[width=0.55\columnwidth]{stresslet_reflection.png}
  \caption{Schematic of the wall reflection of the stresslet flow induced by one particle and its qualitative effect on the other particle. Reproduced from \cite{zurita-gotor_2007} (\lb{Permission???}).}
  \label{fig:stresslet-refl}
\end{figure}

@@

Finally, we note that these observed particle interactions may be superimposed pairwise to infer the collective dynamics of a group of particles in similar conditions.
To illustrate this point, we simulated two rigid particles in a periodic channel (thus mimicking a 1D crystal) and observed a crossover from permanent separation of the particle pair (for $0.32 \lessapprox z_0/H \lessapprox 0.68$) to a trapping state (for $z_0/H \lessapprox 0.32$ or $z_0/H \gtrapprox 0.68$), where $H$ is the channel height (same setup and notation otherwise, cf.\ Figures \ref{fig:itzhak-boris} and \ref{fig:stresslet-refl}).
Qualitatively, the former results from cross-stream migrations that resemble the BG open trajectories, while the latter is due to position swappings with neighbouring particles strongly influenced by the wall.
See \cite{Beatus2006, Janssen2012, Uspal2013} for analogous, more vivid demonstrations.

@@

significant progress of physical understandings of spatial confinement on hydrodynamic interactions in the last two decades \citep{Cui_etal_2002, Cui2004, Diamant_2005, Davit_2008}

first-principles theory based on conservation laws \citep{Diamant}.
q2D.
dipolar interaction, his eq. (8).
The hydrodynamic interaction between the particles exhibits three anomalies. (i) The transverse coupling is negative; i.e., particles exert ``antidrag'' on one another when moving perpendicular to their connecting line. (ii) The interaction decays with interparticle distance r as $1/r^2$, faster than in unconfined suspensions but slower than near a single wall. (iii) At large distances, the pair interaction is independent of concentration within the experimental accuracy. 
range of interactions,

@@

lubrication approximation?

detailed flow field \citep{zhu_gallaire_2016}

>>>>

The preceding section presents the most basic solutions of the Stokes equation in the presence of one particle.
In practice, however, it is rarely the case particles or droplets exist in isolation.
Particles tend to abound; and they often interact with each other through various types of hydrodynamic or non-hydrodynamic mechanisms, giving rise to a multitude of phenomena in natural or artificial conditions.
For example, soap bubbles are always in a cluster due to the interfacial capillary attraction, while the same underlying principle can be applied to manipulate droplet motions on a surface to aid liquid handling \citep{vapour-sensing}.
To offer at least some partial insights on the hydrodynamics, we highlight recent theoretical developments of droplet interactions in bulk microflows, starting from the simplest case of two particles immersed in unbounded simple shear flows.

@@

\begin{figure}%[t]
  \centering
  \includegraphics[width=0.55\columnwidth]{stresslet_reflection.png}
  \caption{Schematic of the wall reflection of the stresslet flow (cf.\ Figure \ref{fig:lets}) induced by one particle and its qualitative effect on the other particle. Reproduced from \cite{zurita-gotor_2007} (\lb{Permission???}).}
  \label{fig:stresslet-refl}
\end{figure}

@@

Finally, we note that these observed particle interactions may be superimposed pairwise to infer the collective dynamics of a group of particles in similar conditions.
To illustrate this point, we simulated two rigid particles in a periodic channel (thus mimicking a 1D crystal) and observed a crossover from permanent separation of the particle pair (for $0.32 \lessapprox z_0/H \lessapprox 0.68$) to a trapping state (for $z_0/H \lessapprox 0.32$ or $z_0/H \gtrapprox 0.68$), where $H$ is the channel height (same setup and notation otherwise, cf.\ Figures \ref{fig:itzhak-boris} and \ref{fig:stresslet-refl}).
Qualitatively, the former results from cross-stream migrations that resemble the BG open trajectories, while the latter is due to position swappings with neighbouring particles strongly influenced by the wall.
See \cite{Beatus2006, Janssen2012, Uspal2013} for analogous and more vivid demonstrations.

@@

significant progress of physical understandings of spatial confinement on hydrodynamic interactions in the last two decades \citep{Cui_etal_2002, Cui2004, Diamant_2005, tlusty, Davit_2008}

start from the lubrication approximation.
show some dimensional analyses.
q2D.

going back to point forcing. far-field approximations.
heuristic arguments based on conservation laws \citep{Diamant}.
dipolar interaction, his eq. (8). very small prefactor. 
\begin{equation}
 \begin{aligned}
   {\bm B}^s({\bm x}) \approx -\frac{\alpha H}{\mu} \bigg( \frac{{\bm I}}{\abs{\bm x}^2} -\frac{ 2{\bm x}{\bm x} }{ \abs{{\bm x}}^4} \bigg),
   \quad \textrm{for} \quad \abs{\bm x} \gg H,
 \end{aligned}
\end{equation}

The hydrodynamic interaction between the particles exhibits three anomalies. (i) The transverse coupling is negative; i.e., particles exert ``antidrag'' on one another when moving perpendicular to their connecting line. (ii) The interaction decays with interparticle distance r as $1/r^2$, faster than in unconfined suspensions but slower than near a single wall. (iii) At large distances, the pair interaction is independent of concentration within the experimental accuracy. 
range of interactions,

soap film \citep{Leonardo_etal_2008, Diamant}
\begin{equation}
 \begin{aligned}
   {\bm B}^f({\bm x}) \approx \frac{1}{4\pi\mu H} \bigg[ \big( \ln(\nicefrac{1}{\kappa r}) -1 \big) {\bm I} +\frac{{\bm x}{\bm x} }{ \abs{{\bm x}}^2} \bigg],
   \quad \textrm{for} \quad \abs{\bm x} \gg H,
 \end{aligned}
\end{equation}

\begin{figure}%[t]
  \centering
  \includegraphics[width=0.49\columnwidth]{dipolar.pdf}
  \includegraphics[width=0.49\columnwidth]{soap.pdf}
  \caption{Flow fields due a moving particle in a Hele-Shaw channel (left) and in a soap film (right). Both systems are appoximately quasi-two-dimensional.}
  \label{fig:q2d}
\end{figure}

@@

detailed flow field \citep{zhu_gallaire_2016}
near-field?
